Symmetric Circuits for Rank Gates

### 2018-04-06 sections/symmetric-circuits.tex
minor revisions to Section 5.  Also inserted (informal) definition of circuit isomorphism in Sec 3 for backward reference.
Most recent changes to the conclusion, with edits all around the paper.

\begin{drem}
  G: In fact, this difficulty is present throughout the paper.
\end{drem}

@@

\begin{definition}[Automorphism]\label{defn:automorphism}
  Let $C = \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a
  $(\mathbb{B},\tau)$-circuit of order $n$ computing a $q$-ary query, and where
  $\mathbb{B}$ is a basis of isomorphism-invariant structured functions. Let
  $\sigma \in \sym_n$ and $\pi: G \rightarrow G$ be a bijection such that
  \begin{myitemize}
  \item for all output tuples $x \in [n]^q$, $\pi \Omega (x) = \Omega (\sigma
    x)$,
  \item for all gates $g \in G$, $\Sigma (g) = \Sigma (\pi g)$,
  \item for each relational gate $g \in G$, $\sigma \Lambda (g) = \Lambda (\pi
    g)$, and
  \item For each pair of gates $g, h \in G$ $W(h,g)$ if and only if $W(\pi h,
    \pi g)$ and for each internal gate $g$ we have that $L(\pi g)$ and $ \pi
    \cdot L(g)$ are isomorphism-equivalent.
  \end{myitemize}
  We call $\pi$ an \emph{automorphism} of $C$, and we say that $\sigma$
  \emph{extends to an automorphism} $\pi$. The group of automorphisms of $C$ is
  called $\aut (C)$.
\end{definition}

@@

\begin{drem}
  Should I prove these are actually equivalence relations? I use that fact, but
  it's very easy to prove.
\end{drem}

@@

\begin{drem}
  G: I think the above paragraph may be getting a bit too far into the weeds.
\end{drem}

@@

\begin{thm}
  Let $\BB$ be a basis of symmetric functions and let $(C_n)_{n \in \nats}$ be a
  family of symmetric circuits defined over the basis $\BB$. Then there exists a
  family of symmetric circuits $(C_n')_{n \in \nats}$ defined over $\BM$ that
  decides the same language. Moreover, the map $C_n \mapsto C_n'$ is
  polynomial-time computable and for each $n \in \nats$, $\vert C_n' \vert \leq
  (5 \cdot \vert C_n \vert + 3) \cdot \vert C_n \vert$.
\end{thm}

>>>>

% \begin{drem}
%   G: In fact, this difficulty is present throughout the paper.
% \end{drem}

@@

\begin{definition}[Automorphism]\label{defn:automorphism}
  Let $C = \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a
  $(\mathbb{B},\tau)$-circuit of order $n$ computing a $q$-ary query, and where
  $\mathbb{B}$ is a basis of isomorphism-invariant structured functions. Let
  $\sigma \in \sym_n$ and $\pi: G \rightarrow G$ be a bijection such that
  \begin{myitemize}
  \item for all output tuples $x \in [n]^q$, $\pi \Omega (x) = \Omega (\sigma
    x)$,
  \item for all gates $g \in G$, $\Sigma (g) = \Sigma (\pi g)$,
  \item for each relational gate $g \in G$, $\sigma \Lambda (g) = \Lambda (\pi
    g)$, and
  \item For each pair of gates $g, h \in G$ $W(h,g)$ if and only if $W(\pi h,
    \pi g)$ and for each internal gate $g$ we have that $L(\pi g)$ and $ \pi
    \cdot L(g)$ are isomorphism-equivalent.
  \end{myitemize}
  We call $\pi$ an \emph{automorphism} of $C$, and we say that $\sigma$
  \emph{extends to an automorphism} $\pi$. The group of automorphisms of $C$ is
  called $\aut (C)$.
\end{definition}
We can equally define an isomorphism between a pair of circuits $C =
\langle G, \Omega, \Sigma, \Lambda, L\rangle$ and  $C' = \langle G',
\Omega', \Sigma', \Lambda', L'\rangle$ as a bijection $\pi: G
\rightarrow G'$ satisfying conditions as above.  We do not usually
need to consider distinct, isomorphic circuits and for this reason we
only formally define automorphsims.

@@

% \begin{drem}
%   Should I prove these are actually equivalence relations? I use that fact, but
%   it's very easy to prove.
% \end{drem}

@@

% \begin{drem}
%   G: I think the above paragraph may be getting a bit too far into the weeds.
% \end{drem}

@@

\begin{thm}
  Let $\BB$ be a basis of symmetric functions and let $(C_n)_{n \in \nats}$ be a
  family of symmetric circuits defined over the basis $\BB$. Then there exists a
  family of symmetric circuits $(C_n')_{n \in \nats}$ defined over $\BM$ that
  decides the same language. Moreover, the map $C_n \mapsto C_n'$ is
  polynomial-time computable and for each $n \in \nats$, $\vert C_n' \vert \leq
  (5 \cdot \vert C_n \vert + 3) \cdot \vert C_n \vert$.
  \label{thm:symmetric-circuits-bound}
\end{thm}
